\subparagraph{Scenario 1: User Registration}
\noindent
\newline
    Bob is a tourist who just came in Gotham city. He discovers that the city has a system of taxi reservation using a mobile application. So he downloads the mobile app and opens it. The first page presented is the login page, but he hasn't an account yet. So he taps the registration button and he is redirected to the registration page. There he inserts his name and surname, his email and his username and password. He decides to leave the address and phone fields empty.
    Before sending the registration form, he accepts the terms and conditions contract, and sends the registration.
    After a while he receives a mail with a link for the confirmation of the account creation.

\subparagraph{Scenario 2: Taxi driver registration}
\noindent
\newline
    Alice is a taxi driver. She wants to participate in the city government project 'myTaxiService'. At her home she enters her browser in the main page of the myTaxiService web site. She isn't registered yet, so the click on the registration button that redirects her to the registration page. Here she enters her personal data, her username, password, and her taxi licence ID. Once filled the registration form, she accepts the terms and conditions of the service and submits the registration. A confirmation mail is sent to her with a link to complete the registration. She clicks it and she is redirected to the login page.

\subparagraph{Scenario 3: User login}
\noindent
\newline
    Charlie has to go to the airport for his holiday trip. At home on his web browser he enters the myTaxiService site. In the login page he enters his username and password, chosen during the registration phase. Once entered correctly the required values, he clicks the login button and visualizes his home page.

\subparagraph{Scenario 4:User login error}
\noindent
\newline
    Daniel wants to enter the myTaxiService site to view the log of all the requests he accepted. In the login page he enters his username and password, but unfortunately they are wrong. So he retries again but writes them wrong again.
    So he decides to try the recovery password system. In the login page he clicks on the 'Recovery' button. The system tells him it sents an e-mail with the new password auto-generated for entering the account.
    After Daniel receives the mail, he retries to enter into the system using the new password. After clicking onto the Login button he visualizes his homepage

\subparagraph{Scenario 5: Activation of taxi service}
\noindent
\newline
    Emily is beginning her work day as a taxi driver. She uses the myTaxiService system to handle the requests for a taxi. To enable her taxi to receive request she has to activate the service via myTaxiService application. Once entered her home page, after the login, she clicks the button for the activation. But she receives an alert regarding the GPS signal: "the system can't track the taxi GPS signal. The service can not be activated". So she turns on the GPS device in the car and retries the activation. This time the system finds the GPS signal and activate her service, putting her taxi in the queue of the city zone where che is in.
    
\subparagraph{Scenario 6: Taxi request}
\noindent
\newline
    It's a sunny day and Michael, who loves swimming, decides to go to the open air swimming-pool of his city. Unfortunately, the swimming-pool is quite far from his home and so he decides to make a taxi request. He remembers that some days ago, he registered to the 'myTaxiService' application. So, he logs in from his mobile application and from his home page, he clicks on the button 'make a taxi request'. The GPS on his mobile device is activated and so, after few seconds, he receives a notification containing the taxi identifier, that has been chosen by the system in order to satisfy his request, and the waiting time expected.

\subparagraph{Scenario 7: Taxi reservation}
\noindent
\newline
    Lorena is planning a visit to the local museum of the city. She loves planning every single detail of her trip and so she decides to make a taxi reservation in advance. She opens the web application of 'myTaxiService' and so she logs in. From the home page, she clicks on 'make a taxi reservation'; then, due to the fact that her GPS is not activated, she selects the origin and the destination of her ride. She has also to specify the date and the hour of the ride. After some seconds, she receives a notification from the application that confirms her reservation and indicates the taxi identifier that will take care of her journey.

\subparagraph{Scenario 8: Taxi driver request acceptance}
\noindent
\newline
    Alessia is a taxi driver, already registered in the system, and she is waiting for a request at the parking of city zone 2. She set her status as 'available' from her taxi driver application. Suddenly, she receives a notification on her device: it's a request from a user. She clicks on the button 'accept' and, after viewing where the user is located, she is ready to go to the origin of the ride.