\subsubsection{Definitions}
	We rewrite some of the definitions that were given in the RASD document and that will be widely used also in this document. 
	\begin{itemize}
		\item PASSENGER: for passenger we mean a person, already registered in the system, who has requested or reserved a taxi either through the web or the mobile applications.
		\item USER: a person who is already registered in the system that can use the application to request or reserve a taxi.
		\item GUEST:  a person who is not registered in the system.
		\item REQUEST: message sent by the user's application to the system in order to require a taxi or make a reservation.
		\item CALL: a task received by the taxi drivers after a user made a request.
		\item TAXI ZONE: for taxi zone we mean a zone that is approximately of 2km2. Each taxi zone has a queue of taxi associated. 
		\item QUEUE: for queue we mean the list of taxi available at a specific moment in a certain zone.
		\item NOTIFICATION: for notification we mean a message that could be send by the system to the user (in order to notify the taxi identifier that will satisfy his request and the waiting time) or by the system to a specific taxi driver (in order to notify that a user has a request or a reservation to satisfy).
		\item RESERVATION: the action of the user to book a taxi followed by a request to the system.
	\end{itemize}

\subsubsection{Acronyms}
	\begin{itemize}
		\item DBMS: Database Management System.
		\item DD: Design Document.
		\item DMZ: demilitarized zone.
		\item GPS: Global Positioning System.
		\item JSON: JavaScript Object Notation.
		\item JPA: Java Persistance API. 
		\item MVC: Model-view-controller.
	    \item RASD: Requirements Analysis and Specification Document.
	    \item REST: Representational state transfer.
		\item SD: Sequence Diagram.
		\item UX: User Experience.
		\item XML: eXtensible Markup Language.
	\end{itemize}