\subsection{Taxi queue management}
This section describes the procedures the system uses to manage the taxi queues.
\newline
The taxi are distributed in the various zones the city is divided in. Each zone has a taxi queue in which there are only taxi whose status is 'AVAILABLE'.
QueueManager and ZoneManager components are responsible for managing the taxi.

The algorithm is executed when one of these events occurs:
\begin{enumerate}
    \item A taxi driver changes his status.
    \item A taxi driver changes zone.
    \item A taxi driver accepts a call.
    \item A taxi driver refuses a call.
    \item A taxi driver sets a call as 'COMPLETED'.
\end{enumerate}
For each event the system behaves in a different way.

The system variables used by this algorithm are:
\begin{itemize}
    \item $Q_i$: the queue list for the zone $i$
    \item $T$: the list of taxi drivers that are not in a queue, but are logged into the system.
\end{itemize}

Whenever the system receives an event $e$ the algorithm is executed.
\subparagraph{Event: taxi driver changes his status}
\begin{itemize}
    \item from 'OFFLINE' or 'NOTAVAILABLE' to 'AVAILABLE': the taxi driver reference is put into the queue $Q_i$ referred to the zone $i$. To find the right zone and queue the algorithm uses the parameters passed to the event $e$, which are: the reference of the taxi driver, his location and the type of event.
    \item from 'AVAILABLE' or 'NOTAVAILABLE' to 'OFFLINE': the taxi driver is removed from the $Q_i$ or the $T$ queues.
    \item from 'AVAILABLE' to 'NOTAVAILABLE': the taxi driver is removed from the queue $Q_i$ and put into the $T$ queue.
\end{itemize}

\subparagraph{Event: taxi driver changes zone}
This event is triggered when the ZoneManager realizes that the taxi driver has changed zone and notifies the QueueManager.
When this event occurs the taxi driver is removed from the $Q_i$ queue list where the taxi is currently in and he is put into the new $Q_k$ queue associated to the new zone he entered.

\subparagraph{Event: taxi driver accepts the call}
When a taxi driver accepts a request, this event is fired. 
The algorithm removes the taxi driver from the $Q_i$ zone and put it into the $T$ queue.

\subparagraph{Event: taxi driver refuses the call}
When a taxi driver refuses a request, this event is fired. 
The algorithm removes the taxi driver from the first position of the $Q_i$ queue and put him in the last position of the same queue.

\subparagraph{Event: taxi driver sets a call as 'COMPLETED'}
When a taxi driver sets a call as 'COMPLETED', he becomes 'AVAILABLE', so he is put at the end of the $Q_i$ queue.