This function type refers to elementary operations that elaborate data coming from the external environment.
\newline
In our system, the External Input operations that concern the general user (either taxi driver or passenger) are:
\begin{itemize}
    \item Sign up into the system. 
	\item Login/Logout.
	\item Change password/information of the account. 
	\item Delete account. 
\end{itemize}
The Login and Logout operations are simple operations, so we can use a simple weight for them: 2 x 3 = 6 FPs. The change account information and the Sign up operation are more difficult, and we gave them a medium complexity: 2 x 4 = 8 FPs.
The Delete account is a complex operation : 6 FPs.
\newline

There are others External Input operations that refer only to taxi drivers:
\begin{itemize}
	\item Notify the system of their availability. 
	\item Accept requests. 
	\item Decline requests. 
	\item Activate/Deactivate taxi service. 
	\item Track their position via GPS. 
\end{itemize}
The tracking operation and the management of the taxi service are simple operations, so they have a simple complexity: 2 x 3 = 6 FPs.
The other 3 operations have a medium complexity : 3 x 4 = 12 FPs.
\newline

There are others External Input operations that refer only to passengers:
\begin{itemize}
	\item Request a taxi. 
	\item Reserve a taxi. 
	\item Delete requests. 
	\item Delete reservations. 
\end{itemize}
The Request and Reservation have a medium complexity: 2 x 4 = 8 FPs. Instead the delete operation are complex operations: 2 x 6 = 12 FPs.
\newline
All these operations have been identified referring to the RASD.\footnote{Section "Overall Description"}