When a taxi driver is visiting his home page in the application, he should be able to activate or deactivate his taxi service sending a notification to the system.
When the system receives the notification from the user application about activating/deactivating the taxi system, it checks if the GPS installed in the car connected to the account is on. If there are no errors the taxi is put into a taxi zone queue/removed from the queue. And the system sends him a notification

\subparagraph{Use case}
\noindent
    \begin{center}
        \begin{longtable}{| l | p{0.6\textwidth} |}
            \hline
            Actor & Taxi Driver \\
            \hline
            Goal & Goal~\ref{g-manage}
            \\
            \hline
            Input condition & A taxi driver enters his account page and tries to change his status. \\
            \hline
            Event Flow & 
                \begin{enumerate}
                	\item The taxi driver changes his status from his account page using the buttons in the account page.
            	\end{enumerate}
            \\
            \hline
            Output condition & The system confirms the change sending a notification to the taxi driver.\\
            \hline
            Exception & 
            \begin{itemize}
               \item If the GPS on the car isn't active, when the taxi driver tries to set is status to "available", the application alerts the user to retry the operation.
            \end{itemize} \\
            \hline
        \end{longtable}
    \end{center}

\subparagraph{Functional requirements}
\noindent
	\begin{itemize}
		\item The activation of the service can occur only if the GPS installed on the car is active, otherwise the taxi driver receives an alert on his application.
		\item If the system can not receive the GPS signal every 5 minutes, it sends a notification to the user.
		\item If the system can not receive the GPS signal for more than 20 minutes, the taxi service is deactivated.
		\item The taxi service can be deactivated only if the user isn't taking a request/reservation.
	\end{itemize} 
