After the login process, users are redirected to their main page. Here they have the possibility to choose different actions to perform.
For example, they can reset their password, change personal information or delete their account.
If the user who reached this page is a generic user, he can choose the option of creating a request or a reservation.
If the user is a taxi driver, there are others types of actions available: for instance, he can view the pending requests sent by the system and accept or decline them.

\subparagraph{Functional requirements}
\noindent
	\begin{itemize}
		\item A generic user can:
		\begin{itemize}
			\item Change password.
			\item Change account information.
			\item Make a taxi request.
			\item Make a Reservation.
			\item Delete requests or reservation.
			\item Visualize all the requests/reservations done.
			\item View the history of all the rides done.
		\end{itemize}
		\item A taxi driver user can:
		\begin{itemize}
			\item Change password.
			\item Change account information.
			\item Delete account.
			\item View the history of all the rides done.
			\item Activate/Deactivate taxi service.
			\item View the pending request.
			\item Track the taxi via GPS.
		\end{itemize}
		
		\item During the 'password changing' phase, the old password should provided with the new one.
		\begin{itemize}
			\item The new password must be an alphanumeric string with at least a number and a uppercase character.
			\item The new password length must be between 8 and 16 characters. 
			\item The new password must be different from the old one.
		\end{itemize}
		\item During the 'account deletion' phase, after the confirmation of the user, a mail is sent to him with a link that allows to deactivate the account.
		\item The deletion account function delete the account but keeps all the user information. The information are kept as history in the DB.
		\item Activate/Deactivate taxi service: the taxi driver use this function to tell the system to activate/deactivate the taxi service adding/removing him from the taxi queues in the city zones.
		\item A request received by a taxi driver is displayed in his main page for one minute, then it is passed to the next user in the city zone queue.
	\end{itemize}