\subsubsection{Definitions}
	In order to avoid confusion, we want to specify the definition of some words that will be often used in our documentation of the project. 
	\begin{itemize}
		\item PASSENGER: for passenger we mean a person, already registered in the system, who has requested or reserved a taxi either through the web or the mobile applications.
		\item USER: a person who is already registered in the system that can use the application to request or reserve a taxi.
		\item GUEST:  a person who is not registered in the system.
		\item REQUEST: message sent by the user's application to the system in order to require a taxi or make a reservation.
		\item CALL: a task received by the taxi drivers after a user made a request.
		\item TAXI ZONE: for taxi zone we mean a zone that is approximately of 2km2. Each taxi zone has a queue of taxi associated. 
		\item QUEUE: for queue we mean the list of taxi available at a specific moment in a certain zone.
		\item NOTIFICATION: for notification we mean a message that could be send by the system to the user (in order to notify the taxi identifier that will satisfy his request and the waiting time) or by the system to a specific taxi driver (in order to notify that a user has a request or a reservation to satisfy).
		\item RESERVATION: the action of the user to book a taxi followed by a request to the system.
		\item TAXI SHARING: the service that allows passengers to share a taxi.
	\end{itemize}

\subsubsection{Acronyms}
	\begin{itemize}
	    \item RASD: Requirements Analysis and Specification Document.
		\item GPS: Global Positioning System.
		\item DBMS: Database Management System.
		\item SD: Sequence Diagram.
	\end{itemize}